---
title: "Final Project"
author: "Dutch"
date: "January 8, 2017"
output: html_document
---

##Data Cleaning and Partition
Load the data and create train and test sets
```{r}

library(data.table)
train <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv', na.strings = c("NA","#DIV/0!",""))
FINAL <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv', na.strings = c("NA","#DIV/0!",""))

library(caret)
inTrain <- createDataPartition(train$classe, p=0.6, list=FALSE)
myTrain <- train[inTrain, ]
myTest <- train[-inTrain,  ]

```


I need to determine which variables are key indicators for certain classes. Only looking at accelerometers on the belt, forearm, arm, and dumbell. I will delete the first 6 variables, as these are irrelevant.  Then, I will remove any variable where there are NAs. 
```{r}
myTrain <- myTrain[,-(1:6)]
myTest <- myTest[,-(1:6)]
FINAL <- FINAL[,-(1:6)]
#Take out NAs
myTrain <- myTrain[, colSums(is.na(myTrain)) == 0]
myTest <- myTest[, colSums(is.na(myTest)) == 0]
FINAL <- FINAL[, colSums(is.na(FINAL)) == 0]

```

##Model Selection and Creation
Model Selection - LETS GO!!  First I will do decision trees.
```{r}
library(rpart)
fit1 <- rpart(classe~., data=myTrain, method="class")
predict1 <- predict(fit1, myTest, type = "class")
confusionMatrix(predict1, myTest$classe)
library(rattle)
fancyRpartPlot(fit1)
```

I can see the Accuracy is .766 on this model.  Next, I will do random forest analysis.
```{r}
library(RColorBrewer)
library(randomForest)
fit2 <- randomForest(classe ~., data = myTrain, method = "class")
predict2 <- predict(fit2, myTest, method = "class")
confusionMatrix(predict2, myTest$classe)
plot(fit2)
```

##Conclusions and Out of Sample Error Rate
Random Forest got me 99.67% accuracy.  This means my predicted out of sample error rate is expected to be 100-99.67 or .33%.